Data Dashboard

### 2020-03-04 analysis/05_market_simulator.Rmd
Fixed the formatting and chart

---
title: "Data Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
runtime: shiny
---

@@

testlevels <- as.data.frame(matrix(0, 12, 1))
testlevels[c(3,4,8),] <- 1
testlevels[11,] <- 22.4
testWeights <- c(.4, .15, .53, .19, .32, .09, .00, .1,.14, .16, -.08, 1.24)
testWeights <- as.data.frame(matrix(testWeights, nrow = 12, ncol = 1))

exp(t(testlevels) %*% as.matrix(testWeights))
####################################################################################

@@

renderTable({
    df()
})

renderTable({
    choice = df()
    t(choice[,3]) %*% as.matrix(intercept_mod[,2])

ai_util <- renderTable({
    choice = df()
    exp(t(choice[,3]) %*% as.matrix(intercept_mod[,2]))

@@

Column {data-width=200 .sidebar}
-------------------------------------------------------------------------------------

```{r Inputs}

Row
------------------------------------------------------------------------------------

```{r plot}
#barchart <- ggplot()

#ggplotly(barchart)
```

Row 
--------------------------------------------------------------------------------------
### Amnesty International Expected Utility

@@

```{r}
renderValueBox({
  choice = df()
  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(gp_exp_util,
           color = "green")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(ox_exp_util,
           color = "teal")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(rc_exp_util,
           color = "maroon")
})
```

Row 
--------------------------------------------------------------------------------------

@@

  ai_rate <- round(1000 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ai_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "#FFC30B"))
})
```

@@

  gp_rate <- round(1000 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(gp_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "green"))
})
```

@@

  ox_rate <- round(1000 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ox_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "teal"))
})
```

@@

  rc_rate <- round(1000 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(rc_rate, 
        min = 0, 
        max = 1000,
        gaugeSectors(colors = "maroon"))
})
```

Row 
--------------------------------------------------------------------------------------

>>>>

---
title: "Data Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

@@

####################################################################################

@@

@@

Row
-------------------------------------

```{r plot}
renderPlotly({
  choice = df()
  ai_exp_util <- round(exp(t(choice[, 3]) %*% as.matrix(intercept_mod[,2])),2)
  gp_exp_util <- round(exp(t(choice[, 4]) %*% as.matrix(intercept_mod[,2])),2)
  ox_exp_util <- round(exp(t(choice[, 5]) %*% as.matrix(intercept_mod[,2])),2)
  rc_exp_util <- round(exp(t(choice[, 6]) %*% as.matrix(intercept_mod[,2])),2)
  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))

  data <- c(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util, ai_rate, gp_rate, ox_rate, rc_rate)
  df <- as.data.frame(matrix(data, 8, 1))
  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  colnames(df) <- c('Value', 'Organization', "Type")

  ggplotly(ggplot(df, aes(y = Value, x = Organization, fill = Type)) +
             geom_col() +
             labs(x="") + 
             #scale_fill_manual(values = c("Amnesty International" = "#FFC30B", "Greenpeace" = "#3fad48", "Oxfam" = "#006633", "Red Cross" = "#660000"))+
             theme(legend.position = "none", axis.text.x = element_text(angle = 10, hjust = 1)) +
             facet_wrap(~Type)
    )
})
```

Row 
-------------------------------------
### Amnesty International Expected Utility

@@

```{r}
renderValueBox({
  choice = df()
  gp_exp_util <- round(exp(t(choice[,4]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(gp_exp_util,
           color = "#3fad48")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  ox_exp_util <- round(exp(t(choice[,5]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(ox_exp_util,
           color = "#006633")
})
```

@@

```{r}
renderValueBox({
  choice = df()
  rc_exp_util <- round(exp(t(choice[,6]) %*% as.matrix(intercept_mod[,2])),2)
  valueBox(rc_exp_util,
           color = "#660000")
})
```

Row 
-------------------------------------

@@

  ai_rate <- round(100 * ai_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ai_rate, 
        min = 0, 
        max = 100,
        gaugeSectors(colors = "#FFC30B"),
        symbol = "%")
})
```

@@

  gp_rate <- round(100 * gp_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(gp_rate, 
        min = 0, 
        max = 100,
        gaugeSectors(colors = "#3fad48"),
        symbol = "%")
})
```

@@

  ox_rate <- round(100 * ox_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(ox_rate, 
        min = 0, 
        max = 100,
        gaugeSectors(colors = "#006633"),
        symbol = "%")
})
```

@@

  rc_rate <- round(100 * rc_exp_util/sum(ai_exp_util, gp_exp_util, ox_exp_util, rc_exp_util))
  gauge(rc_rate, 
        min = 0, 
        max = 100,
        gaugeSectors(colors = "#660000"),
        symbol = "%")
})
```

Row 
-------------------------------------
